Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-09 project.Rmd
fixes and cleanups

```{r cleanup, echo=FALSE}
out_domain <- (seis$min < domain[1] | seis$max > domain[2])
invalid_values <- (seis$min == -1 & seis$max == 1) | (seis$min == 0 & seis$max == 0) | out_domain
cat("Removing", sum(out_domain), "values out of domain,", (sum(invalid_values) - sum(out_domain)), "explicit NA\n")
seis <-
  seis %>%
  mutate(min=replace(min, invalid_values, NA), max=replace(max, invalid_values, NA)) %>%
  drop_na()
# %>% mutate(belgian_second=with_tz(utc_second, "Europe/Brussels"))
remove(out_domain, invalid_values) # free ~350 Mb from RAM
```
## Missing values analysis (seconds)
```{r missing values analysis}
seis.complete <- seis %>% complete(utc_second=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = as.difftime("0:0:1")))
seis.first.second <- min(seis$utc_second)
seis.missing.ids <- which(is.na(seis.complete$min))

seis.present <- length(seis$utc_second)
seis.total <- length(seis.complete$utc_second)
seis.missing <- seis.total - seis.present
cat(seis.present, "present values,", seis.missing, "missing points (", print_dec(seis.present / seis.total * 100, 2), "% /", print_dec(seis.missing / seis.total * 100, 2), "% )\n")

block_start <- NULL
block_end <- NULL
blocks <- data.frame(start=integer(), end=integer())
for (i in 1:length(seis.missing.ids)) {
  if (is.null(block_start)) {
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  } else if ((block_end + 1) == seis.missing.ids[i]) {
    block_end <- seis.missing.ids[i]
  } else {
    blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  }
}
blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
blocks$interval <- seconds(blocks$end - blocks$start + 1)
blocks$start <- seis.first.second + seconds(blocks$start + 1)
blocks$end <- seis.first.second + seconds(blocks$end + 1)
plot(blocks$start, blocks$interval,
     col=ifelse(blocks$interval<3600, "darkgreen", "darkred"),
     main="Consecutive seconds of missing values",
     ylab="Seconds", xlab="Interval start (mm-'yy)",
     xaxt="n", xlim=c(min(seis$utc_second), max(seis$utc_second))
)
axis.POSIXct(1, at=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = "1 month"), format="%m-'%y", cex=0.8)
abline(h=3600, col="green", lty="dotted")
legend("topleft", legend=c("interval >= 1h", "interval < 1h", "1h"), col=c("darkred", "darkgreen", "green"), lty=c(NA,NA,3), pch=c(1,1,NA),cex=0.9, bty="n")
text(x=blocks$start[which(blocks$interval > 3600)], y=blocks$interval[which(blocks$interval > 3600)], labels = paste0(blocks$start[which(blocks$interval > 3600)], " - ", blocks$end[which(blocks$interval > 3600)]), cex=0.9, pos=4)
remove(seis.complete, seis.missing.ids)
```

@@

## Missing values analysis (hours)
```{r missing values hour analysis}
seis.complete <- seis.h %>% complete(utc_hour=seq.POSIXt(from=min(seis.h$utc_hour), to=max(seis.h$utc_hour), by = as.difftime("1:0:0")))
seis.first.second <- min(seis$utc_second)
seis.missing.ids <- which(is.na(seis.complete$mean_movement_s))

seis.present <- length(seis.h$utc_hour)
seis.total <- length(seis.complete$utc_hour)
seis.missing <- seis.total - seis.present
cat(seis.present, "present values,", seis.missing, "missing points (", print_dec(seis.present / seis.total * 100, 2), "% /", print_dec(seis.missing / seis.total * 100, 2), "% )\n")

block_start <- NULL
block_end <- NULL
blocks <- data.frame(start=integer(), end=integer())
for (i in 1:length(seis.missing.ids)) {
  if (is.null(block_start)) {
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  } else if ((block_end + 1) == seis.missing.ids[i]) {
    block_end <- seis.missing.ids[i]
  } else {
    blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  }
}
blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
blocks$interval <- hours(blocks$end - blocks$start + 1)
blocks$start <- seis.first.second + hours(blocks$start + 1)
blocks$end <- seis.first.second + hours(blocks$end + 1)
plot(c(rbind(blocks$start, blocks$end, NA)), rep(hour(blocks$interval), each=3),
     col=ifelse(blocks$interval<3600, "darkgreen", "darkred"),
     main="Consecutive hours of missing values",
     ylab="Hours", xlab="Interval start (mm-'yy)",
     type="l", lwd=10,
     xaxt="n", xlim=c(min(seis$utc_second), max(seis$utc_second))
     )
axis.POSIXct(1, at=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = "1 month"), format="%m-'%y", cex=0.8)
text(x=blocks$start, y=hour(blocks$interval), labels = paste0(format(blocks$start, "%y-%m-%d %H:%M")), cex=0.9, pos=2)
text(x=blocks$end, y=hour(blocks$interval), labels = paste0(format(blocks$end, "%y-%m-%d %H:%M")), cex=0.9, pos=4)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=3)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=1)
remove(seis.complete, seis.missing.ids)

blocks$interval

@@

@@

```{r plot data with (p)acf}
seis.h.24 <- build_ts(seis.h.train, periods = c(24))
seasonplot(seis.h.24, type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.train.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)

plot_grid(
  autoplot(seis.h.train, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = "mean movement (nm)"),
  gghistogram(seis.h.train, add.normal = T) + xlab("mean movement (nm)"),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)

```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)

@@

```{r trend MA}
f <- seasonality.period
weights.s <- c(0.5, rep(1,f-1), 0.5)/f
trend.s <- stats::filter(seasonality.aggregate(seis.h.train), side=2, filter=weights.s)
stats::filter(seasonality.aggregate(seis.h.train), sides=2, filter = weights.s) %>% autoplot()
stats::filter(seasonality.aggregate(seis.h.train) %>% diff(), sides=2, filter = weights.s) %>% autoplot()
stats::filter(seasonality.aggregate(seis.h.train) %>% diff(lag=168), sides=2, filter = weights.s) %>% autoplot()
stats::filter(seasonality.aggregate(seis.h.train) %>% diff() %>% diff(lag=168), sides=2, filter = weights.s) %>% autoplot()
mean((seasonality.aggregate(seis.h.train) %>% diff(lag=168))[(1+(168*4)):(1+(168*6))])

@@

@@

>>>>

```{r cleanup, echo=FALSE}
out_domain <- (seis$min < domain[1] | seis$max > domain[2])
invalid_values <- (seis$min == -1 & seis$max == 1) | (seis$min == 0 & seis$max == 0) | out_domain
cat("Removing", sum(out_domain), "values out of domain,", (sum(invalid_values) - sum(out_domain)), "explicit NA\n")
seis <-
  seis %>%
  mutate(min=replace(min, invalid_values, NA), max=replace(max, invalid_values, NA)) %>%
  drop_na()
# %>% mutate(belgian_second=with_tz(utc_second, "Europe/Brussels"))
remove(out_domain, invalid_values) # free ~350 Mb from RAM
```
## Missing values analysis (seconds)
```{r missing values analysis}
seis.complete <- seis %>% complete(utc_second=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = as.difftime("0:0:1")))
seis.first.second <- min(seis$utc_second)
seis.missing.ids <- which(is.na(seis.complete$min))
#seis.complete$utc_second[seis.missing.ids]
seis.present <- length(seis$utc_second)
seis.total <- length(seis.complete$utc_second)
seis.missing <- seis.total - seis.present
cat(seis.present, "present values,", seis.missing, "missing points (", print_dec(seis.present / seis.total * 100, 2), "% /", print_dec(seis.missing / seis.total * 100, 2), "% )\n")

block_start <- NULL
block_end <- NULL
blocks <- data.frame(start=integer(), end=integer())
for (i in 1:length(seis.missing.ids)) {
  if (is.null(block_start)) {
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  } else if ((block_end + 1) == seis.missing.ids[i]) {
    block_end <- seis.missing.ids[i]
  } else {
    blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  }
}
blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
blocks$interval <- seconds(blocks$end - blocks$start + 1)
blocks$start <- seis.first.second + seconds(blocks$start + 1)
blocks$end <- seis.first.second + seconds(blocks$end + 1)
plot(blocks$start, blocks$interval,
     col=ifelse(blocks$interval<3600, "darkgreen", "darkred"),
     main="Consecutive seconds of missing values",
     ylab="Seconds", xlab="Interval start (mm-'yy)",
     xaxt="n", xlim=c(min(seis$utc_second), max(seis$utc_second))
)
axis.POSIXct(1, at=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = "1 month"), format="%m-'%y", cex=0.8)
abline(h=3600, col="green", lty="dotted")
legend("topleft", legend=c("interval >= 1h", "interval < 1h", "1h"), col=c("darkred", "darkgreen", "green"), lty=c(NA,NA,3), pch=c(1,1,NA),cex=0.9, bty="n")
text(x=blocks$start[which(blocks$interval > 3600)], y=blocks$interval[which(blocks$interval > 3600)], labels = paste0(blocks$start[which(blocks$interval > 3600)], " - ", blocks$end[which(blocks$interval > 3600)]), cex=0.9, pos=4)
remove(seis.complete, seis.missing.ids, seis.present, seis.total, seis.missing, block_start, block_end, blocks)
```

@@

## Missing values analysis (hours)
```{r missing values hour analysis}
seis.complete <- seis.h %>% complete(utc_hour=seq.POSIXt(from=min(seis.h$utc_hour), to=max(seis.h$utc_hour), by = as.difftime("1:0:0")))
seis.first.second <- min(seis$utc_second)
seis.missing.ids <- which(is.na(seis.complete$mean_movement_s))
# seis.complete$utc_hour[seis.missing.ids]
seis.present <- length(seis.h$utc_hour)
seis.total <- length(seis.complete$utc_hour)
seis.missing <- seis.total - seis.present
cat(seis.present, "present values,", seis.missing, "missing points (", print_dec(seis.present / seis.total * 100, 2), "% /", print_dec(seis.missing / seis.total * 100, 2), "% )\n")

block_start <- NULL
block_end <- NULL
blocks <- data.frame(start=integer(), end=integer())
for (i in 1:length(seis.missing.ids)) {
  if (is.null(block_start)) {
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  } else if ((block_end + 1) == seis.missing.ids[i]) {
    block_end <- seis.missing.ids[i]
  } else {
    blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  }
}
blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
blocks$interval <- hours(blocks$end - blocks$start + 1)
blocks$start <- seis.first.second + hours(blocks$start + 1)
blocks$end <- seis.first.second + hours(blocks$end + 1)
plot(c(rbind(blocks$start, blocks$end, NA)), rep(hour(blocks$interval), each=3),
     col=ifelse(blocks$interval<3600, "darkgreen", "darkred"),
     main="Consecutive hours of missing values",
     ylab="Hours", xlab="Interval start (mm-'yy)",
     type="l", lwd=10,
     xaxt="n", xlim=c(min(seis$utc_second), max(seis$utc_second))
     )
axis.POSIXct(1, at=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = "1 month"), format="%m-'%y", cex=0.8)
text(x=blocks$start, y=hour(blocks$interval), labels = paste0(format(blocks$start, "%y-%m-%d %H:%M")), cex=0.9, pos=2)
text(x=blocks$end, y=hour(blocks$interval), labels = paste0(format(blocks$end, "%y-%m-%d %H:%M")), cex=0.9, pos=4)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=3)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=1)
blocks$start
blocks$interval
remove(seis.complete, seis.missing.ids, seis.present, seis.total, seis.missing, block_start, block_end, blocks)

@@

remove(pgram, pgram.data, filter_freq, top95pc, top95freq, top95seas.s, top95seas.h, ratio.color, periodgram)
gc()
```

@@

```{r plot data with (p)acf}
seis.h.24 <- build_ts(seis.h.train, periods = c(24))
seasonplot(seis.h.24, type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.train.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)
remove(seis.h.24)

plot_grid(
  autoplot(seis.h.train, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = "mean movement (nm)"),
  gghistogram(seis.h.train, add.normal = T) + xlab("mean movement (nm)"),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)
```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)

@@

```{r trend MA}
f <- seasonality.period
weights.s <- c(0.5, rep(1,f-1), 0.5)/f
trend.s <- stats::filter(seasonality.aggregate(seis.h.train), side=2, filter=weights.s)

@@

```{r cleanup seasonalities}
remove(matrix, weights, weights.s, ts)
gc()
```

@@

remove(aggregated)

### 2020-06-09 project.after.Rmd
fixes and cleanups

final.training <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
final.testing <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.final.end, force_ms = T)
final.testing <- window(final.testing, start = c(end(final.training)[1] + 1, 1))
if (!is.null(chosen.lambda)) {
  cat(chosen.lambda, BoxCox.lambda(final.training), chosen.lambda == BoxCox.lambda(final.training), "\n")
}

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("final.model")) {
  cat(" fitting...")
  final.model <- Arima(final.training, chosen.model[1:3], chosen.model[4:6], lambda=chosen.lambda)
  cat("DONE")
}
if (!exists("final.forecast")) {
  cat(" forecasting...")
  final.forecast <- forecast(final.model, h=168*8, lambda=chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- final.model
plotting.forecast <- final.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
print(plot_forecast(plotting.forecast) + autolayer(final.testing, series="Original") + ylab("Mean hourly movement (nm)") + xlab("Weeks") + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2))
plots <- show_overlap_and_diff(
  final.training, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

cat("Test set inside the CI\n")
cat("80% CI \t ", print_dec(mean(plotting.forecast$lower[,1] < final.testing & final.testing < plotting.forecast$upper[,1], na.rm = T)*100), "%\n")
cat("95% CI \t ", print_dec(mean(plotting.forecast$lower[,2] < final.testing & final.testing < plotting.forecast$upper[,2], na.rm = T)*100), "%\n")

plots <- show_overlap_and_diff(
  final.testing, plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test set",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2),
                plots[[2]] + geom_vline(aes(xintercept=as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1), linetype=2),
                nrow = 2
                ))

print(accuracy(plotting.forecast, final.testing))
# qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
print(gg_qqplot(plotting.model$residuals) + 
    labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
)

>>>>

final.training <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
final.testing <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.final.end, force_ms = T)
final.testing <- window(final.testing, start = c(end(seis.h.test)[1] + 1, 1))
if (!is.null(chosen.lambda)) {
  cat(chosen.lambda, BoxCox.lambda(final.training), chosen.lambda == BoxCox.lambda(final.training), "\n")
}

fit.name <- paste0("fit", paste0(chosen.model, collapse = ""))
forecast.name <- paste0("forecast", paste0(chosen.model, collapse = ""))
cat("SARIMA(", paste0(chosen.model[1:3], collapse = ","), ")(", paste0(chosen.model[4:6], collapse = ","), ")[", frequency(final.training), "]", sep = "")
if (!exists("full.forecast")) {
  cat(" forecasting...")
  full.forecast <- forecast(models[[fit.name]], h=168*26, lambda = chosen.lambda)
  cat("DONE")
}
cat("\n")
plotting.model <- models[[fit.name]]
plotting.forecast <- full.forecast
print(plotting.model)
print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
print(plot_grid(
  autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.acf,
  autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
  residuals.pacf,
  nrow = 2
))
lockdown.x <- as.integer(as_datetime('2020-03-14T00:00:00') - seis.train.start)/7+1
print(
  plot_forecast(plotting.forecast)
      + autolayer(ts_c(`Before March '20`=seis.h.test, `From March '20`=final.testing))
      + ylab("Mean hourly movement (nm)")
      + xlab("Weeks")
      + geom_vline(aes(xintercept=lockdown.x), linetype=2)
)
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "training set",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))
seis.h.test.len <- length(seis.h.test)
final.testing.len <- length(final.testing)
full.forecast.len <- seis.h.test.len + final.testing.len
full.forecast.before.ids <- 1:seis.h.test.len
full.forecast.after.ids <- (seis.h.test.len+1):full.forecast.len
cat("Test set inside the CI\n")
cat("CI   ", "Overall ", "Before  ", "After  \n")
cat("80 % ",
    print_dec(mean(plotting.forecast$lower[,1] < c(seis.h.test, final.testing) & c(seis.h.test, final.testing) < plotting.forecast$upper[,1], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.before.ids,1] < seis.h.test & seis.h.test < plotting.forecast$upper[full.forecast.before.ids,1], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.after.ids,1] < final.testing & final.testing < plotting.forecast$upper[full.forecast.after.ids,1], na.rm = T)*100),
    "%\n")
cat("95 % ",
    print_dec(mean(plotting.forecast$lower[,2] < c(seis.h.test, final.testing) & c(seis.h.test, final.testing) < plotting.forecast$upper[,2], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.before.ids,2] < seis.h.test & seis.h.test < plotting.forecast$upper[full.forecast.before.ids,2], na.rm = T)*100),
    "% ",
    print_dec(mean(plotting.forecast$lower[full.forecast.after.ids,2] < final.testing & final.testing < plotting.forecast$upper[full.forecast.after.ids,2], na.rm = T)*100),
    "%\n")

plots <- show_overlap_and_diff(
  c(seis.h.test, final.testing), plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test set",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), plots[[2]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), nrow = 2))

plots <- show_overlap_and_diff(
  seis.h.test, window(plotting.forecast$mean, start=c(53,1), end=c(70,168)), xlab=seasonality.xlab,
  base.desc = "test set before lockdown",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

plots <- show_overlap_and_diff(
  final.testing, window(plotting.forecast$mean, start=c(71,1), end=c(78,168)), xlab=seasonality.xlab,
  base.desc = "test set during lockdown",
  compare.desc = paste0("forecast with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="%",
  diff.ylab.sec.accuracy = .01
)
print(plot_grid(plots[[1]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), plots[[2]] + geom_vline(aes(xintercept=lockdown.x), linetype=2), nrow = 2))

print(accuracy(plotting.forecast, c(seis.h.test, final.testing)))
# qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
print(gg_qqplot(plotting.model$residuals) + 
    labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
)
